\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{wasysym}

\name{Matt}{Karimov}
\address{Manchester, UK}
\phone[mobile]{+447803374001}
\email{mattkarimov@outlook.com}
\social[linkedin]{linkedin.com/in/mattkari}
\social[github]{github.com/mattkari}

\begin{document}
%    \makecvtitle
    \maketitle
    \begin{center}
    {\Large \textbf{Quality Automation Specialist}} \\
    \small Java \textbar{} Selenium \textbar{} Cucumber \textbar{} AWS \textbar{} CI/CD
    \end{center}
    Experienced Software QA Engineer with over 5 years in the Banking, Finance, and QA Industry.
    Proficient in both automated and manual testing, with a strong understanding of SDLC, STLC, and Agile Scrum Methodology.
    Demonstrated expertise in backend development, cloud systems, and CI/CD pipelines.
    Adept at collaborating with cross-functional teams, ensuring software quality, and accelerating the release of high-quality software products.
    

    \section{Areas of Expertise}
    \begin{minipage}{0.5\linewidth}
        \begin{itemize}
            \item Automation Testing (Selenium, Cucumber, JUnit, JBehave)
            \item Programming Skills (Java)
            \item Manual Testing
            \item API Testing
            \item Database Testing (SQL, MongoDB)
            \item Understanding of SDLC and STLC
            \item Agile and Scrum Methodology
            \item UI/UX Testing
        \end{itemize}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
        \begin{itemize}
            \item Version Control (e.g., Bitbucket, Git)
            \item CI/CD Tools and Practices
            \item Test Case Management (Jira)
            \item Performance and Load Testing
            \item Effective Communication
            \item Domain Knowledge (Banking, Finance)
            \item Continuous Learning and Adaptability
        \end{itemize}
    \end{minipage}

    \section{Experience}
    \noindent \textbf{Quality Automation Specialist} \hfill \textbf{NatWest Group, UK}  (02/2022 – Present) \\
    \begin{itemize}
        \item Led the development and execution of automation test scripts for SEPA and instant payments in a Dockerized environment, ensuring scalability and reproducibility.
        \item Managed regression test planning with a focus on containerized applications, actively participating in stakeholder meetings for project updates.
        \item Enhanced test coverage through GAP analysis, emphasizing payment processing accuracy and compatibility.
        \item Played a pivotal role in refining testing documentation and practices, aligning with the complexities of instant payments.
        \item Developed Java methods for payment injections using XML, adhering to best coding practices and container standards.
        \item Collaborated with the team to address technical challenges, ensuring seamless integration and functionality of payment modules.
    \end{itemize}
    \small \textit{Bitbucket, Jira, Java, Selenium, Cucumber BDD, Junit, Docker, Cloud Payment Platforms, XML Processing}
    \noindent \textbf{Software QA Engineer} \hfill \textbf{Amplience, UK} (04/2021 – 01/2022) \\
    \begin{itemize}
        \item Run bug triage meetings in Agile Scrum Team to prioritise bugs from the backlogs.
        \item Extracted testable scenarios from user stories and create new test plan and ensure tests are executed and results recorded.
        \item Carried out exploratory testing and gap analysis, integration testing and e2e testing.
        \item Completed validation steps and have a QA voice present in release meetings.
        \item Liaised with stockholders and provide feedback about operations risk areas for integration and system impact.
        \item Designed and implementing automated tests using Selenium Web Driver, Cucumber BDD, Junit and TestNG.
    \end{itemize}
    \small \textit{Java, Ruby, Selenium, Cucumber, Junit, MongoDB, Docker, API Testing, Jira, JSON Scheme}

    \noindent \textbf{Software Development Engineer in Test (SDET)} \hfill \textbf{FleetApps, USA} (05/2020 – 04/2021) \\
    \begin{itemize}
        \item Engaged in Agile Scrum Team practices, formulating test scenarios and cases through SDLC using Git and Github.
        \item Applied Java OOP concepts to craft reusable methods and designed a robust test framework using Selenium, Cucumber BDD, TestNG, Maven, and POM.
        \item Executed comprehensive manual and automated tests across front-end and back-end, aligning products with user specifications.
        \item Conducted varied tests like Smoke, Regression, and UI, leveraging Jenkins on AWS EC2 for enhanced automation.
        \item Undertook detailed API testing with REST Assured Library, Postman, and performed database checks using SQL and JDBC.
        \item Managed defects efficiently using Jira, ensuring clear communication through reports and notifications.
    \end{itemize}
    \small \textit{Java, Selenium, Cucumber, Junit, TestNG, Maven, SQL, API Testing, REST Assured Library, Postman, Git, Jenkins, Agile, POM}



    \noindent \textbf{Complaints Manager} \hfill \textbf{Capita, UK} (11/2017 – 01/2021) \\
    \small Client: \textbf{\textit{Lloyds Banking Group}} \\
    \begin{itemize}
        \item Spearheaded manual testing in banking redress calculations, ensuring the precision of both manual and automated calculators for Asset Finance Payment Protection Insurance claims.
        \item Utilized SQL for data-driven decision-making, enhancing the accuracy and efficiency of claim processes.
        \item Delivered actionable insights from calculator test results, driving product improvements while also serving as a Subject Matter Expert in redress calculations.
        \item Championed training and support for Complaints Managers, reinforcing best practices and knowledge sharing.
        \item Established and managed robust communication channels with customers, addressing and resolving a wide range of banking product complaints with transparency and fairness.
    \end{itemize}
    \small \textit{Manual Testing, SQL Database, Automation, Validation, Verification, Fintech, Outcome Testing}

    \noindent \textbf{Quality Assurance Representative} \hfill \textbf{HSBC, Leeds, UK} (05/2017 – 11/2017) \\
    \begin{itemize}
        \item Conducted manual testing, verification, and validation on intricate redress calculators.
        \item Handled sensitive banking data, performing comprehensive reviews and root cause analyses on payment protection insurance complaints.
    \end{itemize}
    \small \textit{Manual Testing, Validation, Verification, Fintech, SQL Database, Audit Check, Edge, BMM, AES, Creditor, ParamMaint}

    \section*{OTHER EXPERIENCES}

    \noindent \textbf{Branch Manager}, Lighthouse Educational Society, London, UK \hfill 2015 - 2016

    \noindent \textbf{Charity Officer}, Northern Education Society, Newcastle upon Tyne, UK \hfill 2009 - 2011

    \noindent \textbf{Lecturer}, TIU University, Tashkent, Uzbekistan \hfill 2003 - 2004

    \section*{EDUCATION \& CREDENTIALS}

    \noindent \textbf{Full Stack Automation Tester (SDET) Program}, Cydeo, Virginia, USA \hfill 2020

    \noindent \textbf{PhD in Governance and International Affairs}, Durham University, UK \hfill 2018

    \noindent \textbf{MA in Public Administration}, JMI Central University, New Delhi, India \hfill 2006

    \noindent \textbf{BA in Legal Studies}, TIU University, Tashkent, Uzbekistan \hfill 2003


\end{document}
