\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.65in,right=0.75in,top=0.65in,bottom=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{wasysym}

% Single line spacing
\setstretch{0.95}
% Customize the section command
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing{\section}{0pt}{*2}{*1.5}

\begin{document}

% Personal Details
    \begin{center}
        \textbf{\LARGE Matt Karimov} \\
        {\small \address{Manchester, UK} \textbar{}
        \phone{+447803374001} \textbar{}
        \email{mattkarimov@outlook.com} \textbar{}
        \social{linkedin.com/in/mattkari} \textbar{}
        \social{github.com/mattkari}}

        {\Large \textbf{Quality Automation Specialist}}\\
        \small Java \textbar{} Selenium \textbar{} Cucumber \textbar{} AWS \textbar{} CI/CD
    \end{center}

    \section*{Profile}
    Experienced Software Development Engineer in Test (SDET) with a strong background in Java programming and automation testing. Proficient in developing and implementing test strategies using Springboot and Microservices, complemented by expertise in Behavior Driven Development (BDD). Demonstrated ability to enhance software quality and efficiency in fast-paced, technology-driven environments. Passionate about leveraging innovative testing methodologies to drive software excellence in the digital economy.
    \section*{Areas of Expertise}
        \begin{minipage}{0.5\linewidth}
        \begin{itemize}
            \item Automation Testing (Selenium, Cucumber, JUnit, JBehave)
            \item Programming Skills (Java)
            \item Springboot & Microservices
            \item Manual Testing
            \item API Testing, REST Assured, Postman
            \item Database Testing (SQL, MongoDB)
            \item Understanding of SDLC and STLC
            \item Agile and Scrum Methodology
            \item UI/UX Testing
        \end{itemize}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
        \begin{itemize}
            \item Version Control (e.g., Bitbucket, Git, Gitlab)
            \item CI/CD Tools and Practices, Jenkins, Maven
            \item Test Case Management (Jira)
            \item Performance and Load Testing
            \item Effective Communication
            \item Domain Knowledge (Banking, Finance)
            \item Continuous Learning and Adaptability
        \end{itemize}
    \end{minipage}


    \section*{Experience}

    \noindent \textbf{Quality Automation Specialist} \hfill \textbf{NatWest Group, UK}  (02/2022 – Present) \\
    \begin{itemize}
        \item Led and executed API testing projects using Postman, ensuring optimal performance and reliability.
        \item Implemented BDD & TDD methodologies using Cucumber to streamline testing processes. Collaborated with cross-functional teams to deliver technology solutions aligning with business objectives.
        \item Led the development and execution of automation test scripts for SEPA and instant payments in a Dockerized environment, ensuring scalability and reproducibility.
        \item Pioneered the integration of ICON's test framework with Docker, providing consistency across test environments and enhancing test reliability.
        \item Managed regression test planning with a focus on containerized applications, actively participating in stakeholder meetings for project updates.
        \item Enhanced test coverage through GAP analysis, emphasizing payment processing accuracy and compatibility.
        \item Developed and scaled automated testing systems, integrating advanced CI/CD practices to enhance delivery speed and reliability
        \item Developed Java methods for payment injections using XML, adhering to best coding practices and container standards.
        \item Engineered and deployed an advanced data-driven testing framework leveraging BDD methodologies, utilizing dynamic parameterization from feature files.
        \item Collaborated with product managers, developers, and designers to refine testing protocols and ensure alignment with project goals.
        \item Led testing efforts on microservices architectures, ensuring system integrity and performance across multiple service components.
        \item Ensured effective collaboration between development and QA teams, ensuring alignment of test strategies with software development goals.
    \end{itemize}
    \small \textit{Behaviour-Driven Development, Data-driven testing, Gitlab, Bitbucket, Jira, Java, Selenium, JBehave, Cucumber BDD, Junit, Docker, Cloud Payment Platforms, XML Processing}


    \noindent \textbf{QA Automation Engineer} \hfill \textbf{Amplience, UK} (04/2021 – 01/2022) \\
    \begin{itemize}
        \item Championed Agile Scrum practices, leading bug triage meetings and extracting test scenarios from user stories to prioritize and formulate comprehensive test plans.
        \item Utilized Java OOP and Ruby to design and implement a robust test automation framework integrating Selenium, Cucumber BDD, TestNG, Maven, and POM.
        \item Conducted diverse test types including exploratory, gap analysis, integration, e2e, Smoke, Regression, and UI testing, ensuring products align with user requirements.
        \item Played a pivotal role in release meetings, representing the QA perspective, and ensuring validation and feedback loops with stakeholders regarding risk areas and system integration.
        \item Leveraged Jenkins on AWS EC2 for enhanced test automation and performed in-depth API testing with REST Assured Library and Postman.
        \item Managed defects and liaised with stakeholders using Jira, ensuring clear communication and timely resolution.
    \end{itemize}
    \small \textit{Java, Ruby, Selenium, Cucumber, Junit, TestNG, MongoDB, Docker, API Testing, REST Assured Library, Postman, Git, Jenkins, Jira, JSON Schema, Maven, POM, Agile}


    \noindent \textbf{Complaints Manager} \hfill \textbf{Lloyds Banking Group, UK} (11/2017 – 01/2021) \\
%    \small Client: \textbf{\textit{Lloyds Banking Group}} \\
    \begin{itemize}
        \item Spearheaded manual testing in banking redress calculations, ensuring the precision of both manual and automated calculators for Asset Finance Payment Protection Insurance claims.
        \item Utilized SQL for data-driven decision-making, enhancing the accuracy and efficiency of claim processes.
        \item Delivered actionable insights from calculator test results, driving product improvements while also serving as a Subject Matter Expert in redress calculations.
        \item Championed training and support for Complaints Managers, reinforcing best practices and knowledge sharing.
        \item Established and managed robust communication channels with customers, addressing and resolving a wide range of banking product complaints with transparency and fairness.
    \end{itemize}
    \small \textit{Manual Testing, SQL Database, Automation, Validation, Verification, Fintech, Outcome Testing}

    \noindent \textbf{Quality Assurance Representative} \hfill \textbf{HSBC, Leeds, UK} (05/2017 – 11/2017) \\
    \begin{itemize}
        \item Conducted manual testing, verification, and validation on intricate redress calculators.
        \item Handled sensitive banking data, performing comprehensive reviews and root cause analyses on payment protection insurance complaints.
    \end{itemize}
    \small \textit{Manual Testing, Validation, Verification, Fintech, SQL Database, Audit Check, Edge, BMM, AES, Creditor, ParamMaint}

    \section*{OTHER EXPERIENCES}

    \noindent \textbf{Branch Manager}, Lighthouse Educational Society, London, UK \hfill 2015 - 2016

    \noindent \textbf{Charity Officer}, Northern Education Society, Newcastle upon Tyne, UK \hfill 2009 - 2011

    \noindent \textbf{Lecturer}, TIU University, Tashkent, Uzbekistan \hfill 2003 - 2004

    \section*{EDUCATION \& CREDENTIALS}

    \noindent \textbf{Full Stack Automation Tester (SDET) Program}, Cydeo, Virginia, USA \hfill 2020

    \noindent \textbf{PhD in Governance and International Affairs}, Durham University, UK \hfill 2018

    \noindent \textbf{MA in Public Administration}, JMI Central University, New Delhi, India \hfill 2006

    \noindent \textbf{BA in Legal Studies}, TIU University, Tashkent, Uzbekistan \hfill 2003










% ... [More experiences can be added similarly]

\end{document}